Benchmarking on Rigetti architecture

### 2022-10-02 txt/manuscript.tex
realization for fourier case

\usepackage{todonotes}

@@

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
positive semidefinite operators having trace equal to one, will be denoted
$\Omega_d$.  The subset of $M_d$ consisting of unitary matrices will be denoted
by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
$M_{d_2}$, which will be denoted 
\begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism.

Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
In this work we will consider a special class of quantum channels, called unitary channels. A unitary channel
$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called a von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
seen as  a measure-and-prepare quantum channel as follows 
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$

\subsubsection{Diamond norm}
This section defines a special norm on the space of linear mappings, known as 
the diamond norm, and establishes some of its properties. 
Next, we will explain the precise connection between the diamond
norm and the task of quantum operation discrimination.

@@

\begin{equation}
\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}_\Phi  \left( \Id \otimes \sqrt{\rho} \right)  \|_1  \end{equation}

\subsubsection{Discrimination of a quantum operations}

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{succ} =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
\end{equation}

In the case of discrimination between two von Neumann measurements $\PP_U$ and 
$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
unitary matrices of dimension $d$.

@@

Before we proceed to presenting our main results, we need to briefly discuss the
problem of discrimination of unitary channels.  In order to formulate the condition for perfect
discrimination of unitary channels we introduce the notion of numerical range of
a matrix $A \in M_d$, denoted by $W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
\mathbb{C}^d, \;
\;\braket{x}{x}=1\}$. The celebrated Hausdorf-T\"oplitz
theorem states that
$W(A)$ is a convex set and therefore $W(A) =\{\tr A \sigma : \sigma \in \Omega_d
\}$. Let us now recall the well-known result for the
distinguishability of unitary channels.
	Let $U \in \UU_d$ and $\Phi_U: \rho \mapsto U \rho U^\dagger$ be a unitary 
	channel. 
	Then 
	\begin{equation}
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	\end{equation}
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $.

%\begin{proposition}
 Let $U = H \diag(1, e^{i \phi}) H^\dagger$, $\phi \in [0, 2\pi)$ and	let 
 $\Phi_U$ and $\Phi_\Id$ be two unitary channels. The following equation holds 
	\begin{equation}
	\min_{E \in \diaguni_2} \|\Phi_{UE} - 
	\Phi_\Id\|_\diamond = \|\Phi_{U} - 
	\Phi_\Id\|_\diamond
	\end{equation}
%\end{proposition}

@@

\section{Illustrative Examples}

Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
Assume that the unitary matrix $U$ is of the form 
\begin{equation}
U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this section we present theoretical probability of correct 
discrimination between these measurements. Moreover, we create the optimal 
theoretical strategy of their discrimination. 
Such a probability can be calculated using Holevo-Helstrom theorem and 
Theorem 1 from~\cite{puchala2018strategies}. 
This probability will be calculated in 
subsection~\ref{sec:example_theoretical_probability}. Later, we will 
discuss the realization of this scheme in 
subsection~\ref{sec:example_realization}. For such realization, we 
will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
and final measurement (see sec.~\ref{sec_example_final_measurement}).

@@

$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then 

@@

@@

\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
\\ 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
\right\|_1  \\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
\\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
\end{split}
\end{equation}
One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
\ket{y}$ the following equation holds~\cite{watrous} 
\begin{equation}
\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
\beta |\braket{x}{y}|^2}.
\end{equation}
By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
\ket{i} \|}$ we obtain 
\begin{equation}
	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
\end{equation}
\todo[inline]{dokonczyc}
Let us take  $\rho_0 =   \frac{1}{2}  	
\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
\begin{equation}
\begin{split}
||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
&= \sum_{i=0}^1  
\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
4|\bra{i}\rho_0\ket{u_i}|^2}  \\
&= \sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} 
\\ 
&=\sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} 
\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
&= \sum_{i=0}^1  \sqrt{
\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + e^{i \phi}}{2}\right|^2}  \\
&= \sum_{i=0}^1\braket{i}{i} \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
&= \frac{|1-e^{i \phi }|}{2}.
\end{split}
\end{equation}
Due to that, we know  
that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem 
of discrimination between 
$\PP_{\Id} $ and $\PP_U$, where 
$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
).

\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond  
&=  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
\Id \otimes \sqrt{\rho} \right) \|_1 \\
&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
\end{split}
\end{equation}
So we obtain that \begin{equation}
\ket{\psi_{AB}} =   | \sqrt{\rho}^\top \rangle  \rangle = \frac{1}{\sqrt{2} } | 
\Id_2 \rangle \rangle, 
\end{equation}
which completes the proof.
\end{proof}

@@

\subsubsection{Final measurement}\label{sec_example_final_measurement}
In this subsection we will derive exact form of the final measurement in the
problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
for $U = H \diag(1, e^{i \phi}) H^\dagger$, where $\phi \in [0, 2\pi)$.

\begin{proposition}
	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
	2\pi)$.  
The  final measurement has the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger,
\end{split}
\end{equation}
where for each $\phi \in \mathbb{R}$,  the controlled unitaries $V_0$ and $V_1$ 
have the form
\begin{equation}
V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
\end{equation}
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) 
&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
\end{equation}
\end{proposition}

\begin{proof}
From Proposition~\ref{prop-discrim} we have the form of discriminator given by
\begin{equation}
\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
\rangle \rangle. 
\end{equation}
From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
Let us define 
\begin{equation}
X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
\otimes \Id_2 \right)(\proj{\psi}).
\end{equation} 
We consider the Hahn-Jordan decomposition. Let 
\begin{equation}
X = P - Q
\end{equation}
where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
\begin{equation}
\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
\end{equation}
and 
\begin{equation}
\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
\end{equation}
Hence, we define $V_0$ such that
\begin{equation}
\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
\end{equation}
and $V_1$ such that
\begin{equation}
\begin{cases} 
V_1 \ket{y_p} = \ket{0} \\ 
V_1 \ket{y_q} = \ket{1}
\end{cases}. 
\end{equation}
For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
follows (see also \texttt{one-qubit.nb}).
The unitary $V_0$ has the form
\begin{equation}
V_0 = \left(
\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
\end{array}
\right),
\end{equation}
whereas the unitary  $V_1$  has the form
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
\end{equation}
for all $\phi \in [0,2\pi)$. 
Finally, we obtain the measurement $\mu$ of the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger.  
\end{split}
\end{equation}

@@

\section{Implementation}
In this section we will compare theoretical probability of correct 
discrimination between these measurements and the realization on real devices.
\todo[inline]{TU WYNIKI PRAKTYTCZNE }
\todo[inline]{tu rozklad i obwody}

@@

 \section{}
 \label{}

 References:
 If you have bibdatabase file and want bibtex to generate the
 bibitems, please use

  \bibliographystyle{elsarticle-num} 
  \bibliography{<your bibdatabase>}

 else use the following coding to input the bibitems directly in the
 TeX file.

 \bibliographystyle{ieeetr}
 \bibliography{rigetti}

>>>>

\usepackage{todonotes} 
\usepackage{url}

@@

Let $M_{d_1,d_2}$ be the set of all matrices of dimension $d_1 \times d_2$ over
the field $\mathbb{C}$. For  simplicity, square matrices will be denoted by
$M_d$.  The subset of $M_d$ consisting of Hermitian matrices of dimension $d$
will  be  denoted  by $\HH_d$,  while  the  set  of  positive semidefinite
matrices of dimension $d$ by $\HH_d^+$. The set of quantum states, that is
positive semidefinite operators having trace equal to one, will be denoted
$\Omega_d$. 
 The subset of $M_d$ consisting of unitary matrices will be denoted
by $\UU_d$, while its subgroup of diagonal unitary operators will be denoted by
$\DD \UU_d$.  We will also need a linear mapping transforming $M_{d_1}$ into
$M_{d_2}$, which will be denoted 
\begin{equation}
\Phi: M_{d_1 } \rightarrow M_{d_2}.
\end{equation} 
There
exists a bijection between introduced linear mappings $\Phi$ and set of matrices $M_{d_1d_2}$,  known as the Choi-
Jamio{\l}kowski isomorphism. 
For a given linear mapping $\Phi_M$ corresponding  Choi operator $\mathcal{J}(\Phi)$ is explicitly written as 
\begin{equation}
\mathcal{J}(\Phi) \coloneqq \sum_{i,j=1}^{d- 1} \Phi(\ketbra{i}{j}) \otimes \ketbra{i}{j}. \end{equation}
Finally, we introduce a special subset of all mappings $\Phi$, called quantum channels, which are completely positive
and trace preserving (CPTP).
In this work we will consider a special class of quantum channels, called unitary channels. Let $U \in \UU_d$ be a unitary operator. A unitary channel
$\Phi_{U}$ is defined as $\Phi_U(\cdot) = U \cdot U^\dagger$ for  $U \in 
\UU_d$. A general quantum
measurement, that is a positive operator valued measure (POVM) $\PP$ is a
collection of positive semidefinite operators $\{E_1, \ldots, E_m \}$ called
\emph{effects}, which sum up to identity, \ie $ \, \, \sum_{i=1}^m E_i = \1$. If
all the effects are rank-one projection operators, then such a measurement is
called a von Neumann measurement. Every von Neumann measurement can be
parameterized by a unitary matrix and hence we will use the notation $\PP_{U}$
for a von Neumann measurement with effects $\{\proj{u_0}, \ldots, \proj{u_{d-1}}\}$,
where $\ket{u_i}$ is the $i+1$-th column of the unitary matrix $U$. The action of
quantum measurement $\PP_{U}$ on some state $\rho \in \Omega_d$ can be
seen as  a measure-and-prepare quantum channel as follows 
$
\PP_{U} : \rho \rightarrow \sum_{i=0}^{d-1} \bra{u_i} \rho \ket{u_i} \proj{i}.
$

\subsubsection{Diamond norm and the task of discrimination between quantum operators}
This section defines a special norm on the space of linear mappings, known as 
the diamond norm, and establishes some of its properties. 
Next, we will explain the precise connection between the diamond
norm and the task of quantum operation discrimination.

@@

The celebrated result by Helstrom~\cite{helstrom1976quantum} gives the optimal  probability of correct discrimination between two quantum operations, $\TT$  and $\SS$, 
in terms of their distance with the use of the diamond norm
\begin{equation}
p_{\text{succ}}(\TT, \SS) =  \frac12 + \frac14 \| \TT - \SS \|_\diamond.
\end{equation}
In the case of discrimination between two von Neumann measurements $\PP_U$ and 
$\PP_\Id$ we know that (from Theorem 1 \cite{puchala2018strategies})
\begin{equation}
\|\PP_U - \PP_\Id\|_\diamond = \min_{E \in \diaguni_d} \|\Phi_{UE} - 
\Phi_\Id\|_\diamond,
\end{equation}
where $\Phi_U$ is unitary channel and $\diaguni_d$ be the set of diagonal 
unitary matrices of dimension $d$.

@@

Before we proceed to presenting our main results, we need to briefly discuss the
problem of discrimination of unitary channels.  For this purpose, we introduce the notion of numerical range of
a given matrix $A \in M_d$. The set \begin{equation}
W(A) =\{\bra{x}A\ket{x}: \ket{x} \in 
\mathbb{C}^d, \;
\;\braket{x}{x}=1\}.
\end{equation}   
is the numerical range of $A$.
The detailed properties of the numerical range and its generalizations we can see on the website~\cite{nr}.

 Let us now recall the well-known result for the
distinguishability of unitary channels.
	Let $U \in \UU_d$ and $\Phi_U$ be a unitary 
	channel. 
	Then, the following equation holds
	\begin{equation}
	\| \Phi_U  - \Phi_{\1} \|_\diamond = 2 \sqrt{1-\nu^2},
	\end{equation}
	where $\nu = \min_{x \in W(U^\dagger)} |x|  $. And hence the optimal probability to discriminate two unitary channel is given by 
	\begin{equation}
	p_{\text{succ}}(\Phi_U, \Phi_\Id) = \frac{1}{2} + \frac{1}{2} \sqrt{1-\nu^2}.
	\end{equation}

@@

\section{Illustrative Example}

Let us focus on single-qubit von Neumann measurements $\PP_\1$ and $\PP_U$.
Assume that the unitary matrix $U$ is of the form 
\begin{equation}
U = H 
\left(\begin{array}{cc}1&0\\0&e^{i \phi}\end{array}\right)  H^\dagger
\end{equation}
%\begin{equation}
%U = H \diag (1, \ee^{\ii \phi}) H^\dagger,
%\end{equation}
where $H$ is the Hadamard matrix of dimension two and $\phi \in [0, 2 \pi)$.
In this section we present theoretical probability of correct 
discrimination between these measurements. Moreover, we create the optimal 
theoretical strategy of their discrimination. 
The otimal probability will be calculated in 
subsection~\ref{sec:example_theoretical_probability}. Later, we will 
discuss the realization of this scheme in 
subsection~\ref{sec:example_realization}. For such realization, we 
will need the proper input state, (see sec.~\ref{sec:example_discriminator}) 
and final measurement (see sec.~\ref{sec_example_final_measurement}).

@@

$\Phi_U$ and $\Phi_\Id$ be two unitary channels. Then, the following equation holds 

@@

\todo[inline]{spr dowod}

@@

For Hermitian-preserving maps \cite{watrous} the diamond norm may be expressed as
\| \Phi  \|_\diamond =  \max_{\rho \in \Omega_d} \| \left( \Id \otimes \sqrt{\rho} \right) \mathcal{J}(\Phi)  \left( \Id \otimes \sqrt{\rho} \right)  \|_1.  \end{equation}
\| \PP_{U} - \PP_{\Id}  \|_\diamond 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
J(\PP_{U} - \PP_{\Id} )  \left( \Id \otimes \sqrt{\rho} \right)  \right\|_1   
\\ 
& =  \max_{\rho \in \Omega_2} \left\| \left( \Id \otimes \sqrt{\rho} \right) 
\sum_{i=0}^{1} \proj{i} \otimes \left( \proj{u_i} - \proj{i} \right)^\top  
\right\|_1  \\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1} \proj{i} \otimes 
\sqrt{\rho}  \left( \proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1  
\\ 
& = \max_{\rho \in \Omega_2} \left\| \sum_{i=0}^{1}\sqrt{\rho}  \left( 
\proj{u_i} - \proj{i} \right)^\top \sqrt{\rho}  \right\|_1
One can prove that for all $\alpha, \beta \ge 0 $, and unit vectors $\ket{x}, 
\ket{y}$ the following equation holds~\cite{watrous} 
\| \alpha \proj{x} - \beta\proj{y} \|_1 = \sqrt{(\alpha + \beta)^2 - 4\alpha 
\beta |\braket{x}{y}|^2}.
By taking $\ket{x} = \frac{\sqrt{\rho} \ket{\bar{u_i}}}{\| \sqrt{\rho} 
\ket{\bar{u_i}} \|}$ and $ \ket{y} = \frac{\sqrt{\rho} \ket{i}}{\|\sqrt{\rho} 
\ket{i} \|}$ we obtain 
	\| \PP_{U} - \PP_{\Id}  \|_\diamond  = \max_{\rho \in \Omega_2} 
	\sum_{i=0}^{1} \sqrt{\left( \bra{u_i} \rho \ket{u_i} + \bra{i} \rho \ket{i 
	}\right)^2 - 4 | \bra{u_i} \rho \ket{i} |^2}.
\todo[inline]{dokonczyc}
Let us take  $\rho_0 =   \frac{1}{2}  	
\left(\begin{array}{cc}1&0\\0&1\end{array}\right)  $,   we obtain
||\mathcal{P}_U - \mathcal{P}_{\1}||_\diamond 
&= \sum_{i=0}^1  
\sqrt{\left(\bra{u_i}\rho_0\ket{u_i} + \bra{i} \rho_0 \ket{i} \right)^2 - 
4|\bra{i}\rho_0\ket{u_i}|^2}  \\
&= \sum_{i=0}^1  \sqrt{ \braket{i}{i}^2 -  \left| \bra{i}  U \ket{i }\right|^2} 
\\ 
&=\sum_{i=0}^1  \sqrt{\braket{i}{i}^2 -  \left| 1 \cdot \bra{i} \proj{u_1} 
\ket{i} + e^{i \phi} \cdot\bra{i}  \proj{u_2}\ket{i}\right|^2} \\
&= \sum_{i=0}^1  \sqrt{
\braket{i}{i}^2 -\braket{i}{i}^2\left| \frac{1 + e^{i \phi}}{2}\right|^2}  \\
&= \sum_{i=0}^1\braket{i}{i} \sqrt{1 -\left| \frac{1+ e^{i \phi}}{2}\right|^2 } 
= 2 \sqrt{1 -\left| \frac{1+e^{i \phi}}{2}\right|^2 } \\
&= \frac{|1-e^{i \phi }|}{2}.
Due to that, we know  
that $| \sqrt{\rho}^{\top} \rangle \rangle$ is the discriminator of the problem 
of discrimination between 
$\PP_{\Id} $ and $\PP_U$, where 
$ U =  H \diag(1, e^{i \phi}) H^\dagger$ (from definition of diamond norm 
).

\begin{equation}
\begin{split}
\| \PP_{U} - \PP_{\Id}  \|_\diamond  
&=  \| \left( \Id \otimes \sqrt{\rho} \right) J(\PP_{U} - \PP_{\Id} )  \left( 
\Id \otimes \sqrt{\rho} \right) \|_1 \\
&= \left\| ( (\PP_{U} - \PP_\Id) \otimes \Id) \left(  | \sqrt{\rho}^\top 
\rangle \rangle \langle \langle \sqrt{\rho}^\top | \right) \right\|_1.
\end{split}
\end{equation}
So we obtain that \begin{equation}
\ket{\psi_{AB}} \coloneqq  | \sqrt{\rho}^\top \rangle  \rangle 
\end{equation}
and hence we have 
\begin{equation}
\ket{\psi_{AB}}= \frac{1}{\sqrt{2} } | 
\Id_2 \rangle \rangle, 
\end{equation}
which completes the proof.
\end{proof}

@@

\subsubsection{Conditional measurement}\label{sec_example_final_measurement}
In this subsection we will derive exact form of the conditional measurement in the
problem of discrimination of von Neumann measurements $\PP_U$ and $\PP_{\Id}$
for $U = H \diag(1, e^{i \phi}) H^\dagger$, where $\phi \in [0, 2\pi)$.

\begin{proposition}
	Consider the problem of discrimination between von Neumann measurements $\PP_U$ 
	and $\PP_\1$, $U = H\diag(1, e^{i \phi}) H^\dagger $ and $\phi \in [0, 
	2\pi)$.  
The  conditioned measurement has the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger,
\end{split}
\end{equation}
where for each $\phi \in \mathbb{R}$,  the controlled unitaries $V_0$ and $V_1$ 
have the form
\begin{equation}
V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
\end{equation}
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) 
&  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
\end{equation}
\end{proposition}

\begin{proof}
	\todo[inline]{spr dowod}
From Proposition~\ref{prop-discrim} we have the form of discriminator given by
\begin{equation}
\ket{\psi} = | \sqrt{\rho}^\top \rangle \rangle = \frac{1}{\sqrt{2}} |\Id_2 
\rangle \rangle. 
\end{equation}
From Holevo-Helstrom theorem  we constrain a measurement $\mu$.  
Let us define 
\begin{equation}
X  = \left( \PP_U \otimes \Id_2 \right)(\proj{\psi}) -  \left( \PP_\Id 
\otimes \Id_2 \right)(\proj{\psi}).
\end{equation} 
We consider the Hahn-Jordan decomposition. Let 
\begin{equation}
X = P - Q
\end{equation}
where $P, Q \ge 0 $. Observe, that $P $ and $Q$ are block-diagonal. 
So, let us define projectors $\Pi_P$ and $\Pi_Q$ onto  $\text{im}(P)$ and $\text{im}(Q)$, 
respectively. Then  $\Pi_P$ and $\Pi_Q$ have the following forms
\begin{equation}
\Pi_P = \left(\begin{array}{cc}\proj{x_p}&0\\0&\proj{y_p}\end{array}\right) 
\end{equation}
and 
\begin{equation}
\Pi_Q = \left(\begin{array}{cc}\proj{x_q}&0\\0&\proj{y_q}\end{array}\right). 
\end{equation}
Hence, we define $V_0$ such that
\begin{equation}
\begin{cases} V_0 \ket{x_p} = \ket{0} \\ V_0 \ket{x_q} = \ket{1} \end{cases}
\end{equation}
and $V_1$ such that
\begin{equation}
\begin{cases} 
V_1 \ket{y_p} = \ket{0} \\ 
V_1 \ket{y_q} = \ket{1}
\end{cases}. 
\end{equation}
For the discrimination task between $\PP_{U}$ and $\PP_{\Id}$, where $U = H 
\diag(1, e^{i \phi })H$, the explicit form of $V_0$ and $V_1$ is given as 
follows (see also \texttt{one-qubit.nb}).
The unitary $V_0$ has the form
\begin{equation}
V_0 = \left(
\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i 
\cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - 
\phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)
\end{array}
\right),
\end{equation}
whereas the unitary  $V_1$  has the form
\begin{equation}
V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i 
\sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} 
\right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right)
\end{equation}
for all $\phi \in [0,2\pi)$. 
Finally, we obtain the measurement $\mu$ of the form
\begin{equation}
\begin{split}
\mu(0) = \proj{0} \otimes V_0 \proj{0} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{0} V_1^\dagger  \\ 
\mu(1) = \proj{0} \otimes V_0 \proj{1} V_0^\dagger +  \proj{1} \otimes V_1 
\proj{1} V_1^\dagger.  
\end{split}
\end{equation}

@@

\section{Implementation}
In this section we will compare theoretical probability of correct 
discrimination between these measurements and the realization on real devices.
\todo[inline]{TU WYNIKI PRAKTYTCZNE }

\subsection{Native case}

\subsection{IBMQ}

\subsection{Lucy}

\subsection{Rigetti}

@@
